Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-04 edubots_surveys.Rnw
Incorporate the local "Elvira" experience, refs #6
It's not totally related, but it was a chatbot and there were similar
experiences reflected in the SoA already.

Also, closes #1 since bibliography is probably complete already.

In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor. In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class. This is why many students prefer to remain silent and ask their question later via email. 
However, this means a waste of time and a delay of hours or even days to get the teacher's answer.
Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
Moreover, using an automated system such as a chatbot allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.

@@

Several higher education chatbots' evaluation studies were undertaken. For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform. Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}. The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
) answers students' frequently asked questions about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions.

>>>>

In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor. In fact, in many cases, students suffer from stress when they have to ask a question in front of the entire class. This is why many students prefer to remain silent and ask their question later via email. 
However, this means a waste of time and a delay of hours or even days to get the teacher's answer; it does not scale well with the size of the class.
Chatbot technology has a potential to fill the gap between teacher and students, helping them to solve questions and carry out a dynamic and autonomous learning \cite{Griol2014,kim2020}.
Moreover, using an automated system such as a chatbot allows the teacher to detect the most demanded topics, and on which he or she should consequently place more emphasis in class.

@@

Several higher education chatbots' evaluation studies were undertaken. For instance, an evaluation review study presented by \cite{Smutny2020} examined 47 educational chatbots implemented in Facebook Messenger with the focus to identify characteristics and quality metric such as language, subject matter and platform. Another study aimed to categorise educational chatbots according to their purpose into service-oriented and teaching-oriented \cite{perez2020rediscovering}. The first category includes those that provide service support such as the chatbot Ask Holly (University of Durham, 2021) % We probably need a reference for this - JJ
and Dina \cite{santoso2018dinus}, both chatbots respond to students' questions about enrolment and registration. Ask L.U. (Lancaster University, 2019 % Another reference
) answers students' frequently asked questions about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot} and Differ (Differ, 2021) facilitate breaking the ice between new students by introducing them to each other.  \cite{ranoliya2017chatbot} proposed a generic chatbot for university students that is able to answer their frequently asked questions; for some time, the University of Granada had ELVIRA as a chatbot in their main page \cite{MOREO20129}. Besides being able to answer pre-established (frequent) questions, it did so from the main University of Granada using an inset character, voiced by a real person, who lip-synched the answers. The emphasis in this case, however, was on the authenticity of the synchronization more than in making the update of questions and answers simpler, or more interactive, using actual messaging platforms. In most cases, using the inset search engine was able to give you more up-to-date and accurate answers.
